\documentclass{article}

\usepackage{color}
\usepackage{fullpage}

\begin{document}
	\begin{center}	
		{\Huge \bf Svit Architecture} \\
		Daniel Lovasko
	\end{center}	
	\vskip\medskipamount 

	\section*{Renderer}
	\subsection*{Settings}

	\section*{Engine}
	\subsection*{Cosine Debugger}
	The most simple engine. Its sole purpose is to render the scene at highest
	speed without any materials or lights, just to be able to check the object
	presence, position and visibility. Each color is defined as the absolute
	value of the {\tt cos}ine of the angle between the ray direction and the
	normal vector defined for the solid at the intersection point.

	\section*{Node}
	All scenes are composed of {\tt Node} objects. {\tt Node} is either a {\tt
	Group} descendant or {\tt Solid} descendant.
	\subsection*{Group}
	{\tt Group}s are organized in a tree fashion. Each {\tt Group} can hold as
	many {\tt Group}s or {\tt Solid}s as desired. Only member function desired by
	the abstract class {\tt Group} is the {\tt add}, which has to be implemented
	by each {\tt Group} implementation.
	\subsubsection*{SimpleGroup}
	Basic implementation, that only calls the ray intersection function on all
	its {\tt Node}s that it contains. After simply harvesting all of the
	intersections, {\tt SimpleGroup} returns them untouched.
	\subsection*{Solid}
	{\tt Solid} represents the set of actual geometry primitives. All of the {\tt
	Solid} descendants shall be visible objects, as opposed to {\tt Group}
	objects, which are mere abstract data structures.
	\subsubsection*{Infinite Plane} Defined by two variables: a random {\tt
	Point3} on the plane and a normal ({\tt Vector3}). An object of infinite area
	and volume, unlimited in two directions. 

	\section*{Image}

	\section*{Intersection}

	\section*{World}

	\section*{Camera}
	An object stored inside the {\tt World} that is used to generate rays that
	are afterwards shoot into the scene. Each {\tt Camera} type needs only to
	override the function {\tt get\_ray}.
	\subsection*{Perspective Camera}
	Basic type of {\tt Camera} that is defined by 5 attributes: its {\tt
	position}, {\tt forward} vector which denotes where is the camera"looking",
	{\tt up} vector that indicates where is the top of the world, {\tt area}
	containing implicitly the aspect ratio of the image and its dimensions.
	Finally the {\tt horizontal\_angle} defining the opening horizontal angle in
	radians of the camera.
	It is important to note, that vectors {\tt forward} and {\tt up} have to be
	perpendicular for the {\tt PerspectiveCamera} to operate as expected.

	\section*{Hashing}
	Each class or struct in the project has defined its hashing function. The
	hash is obtained by hashing the common types as {\tt float} or {\tt int} and
	then combining them together with the {\tt hash\_combine} function.
	Hashes are used to verify the data integrity sent over network.

	\section*{std::cout}
	\section*{Serialization}
	\section*{Basic Geometry}
	\subsection*{SIMD Optimization}
	\subsubsection*{x86}

	\section*{Animation}

	\section*{Networking}

	\section*{Super-sampling}
	\subsection*{Random jitter}
	\subsection*{Poisson}

\end{document}

